WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-08-10 ms.tex
WIP: Add some more future work stuff

One immediately pressing direction for future work is to address the issue of sub\nobreakdashes-threshold signals, as this will be a major issue when Advanced Virgo comes online in 2016\nobreakdashes--2017. Using the full \ac{SNR} time series in place of the autocorrelation function seems like a promising avenue; implementing this requires some infrastructure changes to both the matched filter pipeline and \ac{BAYESTAR}.

>>>>

One immediately pressing direction for future work is to address the issue of sub\nobreakdashes-threshold signals, as this will be a major issue when Advanced Virgo comes online in 2016\nobreakdashes--2017. Using the full \ac{SNR} time series in place of the autocorrelation function seems like a promising avenue; implementing this requires some infrastructure changes to both the matched filter pipeline and \ac{BAYESTAR}. Along these lines, we refer the reader to \cite{PankowRapidPE} for a similar, non-\ac{MCMC} approach to rapid exploration of the full parameter space.

Although the response time of \ac{BAYESTAR} has been driven by the anticipated timescales for kilonova and afterglow emission, a recurring question is whether there is any detectable \ac{EM} signal in the seconds before, during, and after the merger itself. An obvious example would be prompt gamma\nobreakdashes-ray emission, though more exotic ...

Since the \ac{GW} inspiral signal is in principal detectable for up to hundreds of seconds before merger, one could imagine positioning rapidly slewing instruments to search for prompt emission ...
